---
title: "Lab 6: Poisson Lab"
editor: visual
execute: 
  message: false
  warning: false
---

# LAB 6 - Poisson

1.  To complete this lab:

-   Load packages

```{r}
library(MASS) # must be loaded before tidy or chaos will ensue
library(tidyverse)
library(marginaleffects)
library(ggeffects)
library(easystats)
```

-   Download the dataset:

```{r}
data <- read_delim("https://raw.githubusercontent.com/jgeller112/psy504-advanced-stats/main/slides/Poisson/data/2010.csv")

```

-   Read the preregistration document in the repo (preregis.qmd)

    -   Look at the `2010 Dataset Coder.pdf` for information about vars and missing labels.

-   In a separate .qmd document:

    -   Determine what test to run: Poisson or negative binomial (include all necessary code and checks to support this decision).

    -   Write up your results in a paragraph or two making sure you discuss:

        -   Missing data information (how much is there overall? Per variable?)

        -   The test you ran and why

        -   Model fit

            -   A discussion of the effects in the model (include all relevant statistics)

        -   A figure focusing on only one of the predictors in each model (i.e., the one that is most interesting to you)

-   Upload the .qmd and html (Results + Figures) to Github
